\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-24 paper.tex
testbed description

\section{Evaluation} \label{evaluation}
In this section, we use a small testbed and larger scale trace driven simulations  to evaluate the performance of $\mathsf{BATE}$. 
On the testbed, we also implement two TE algorithms, i.e., FFC \cite{FFC} and TEAVAR \cite{Teavar}. 
For simulation, we implement more algorithms, including xxx. 
All codes for our implementation and evaluation will be published, 
so that interested readers can use them in other environments or make further improvements.

@@

\subsubsection{A public cloud example}
We firstly evaluate a public cloud case.
Assume tenants arrive at the public cloud under poisson process with mean arrival rate 2 every minute and the duration of each bandwidth demand is under exponential distribution with a mean of 5 minutes.
Bandwidth demands between each node pair are under uniform distribution between 10Mbps and 50Mbps.
Every 1Mbps is sold 1$\$$.
%The profit of each tenant (i.e., $w_i$) is proportional to his/her total bandwidth demand.
Availability targets and refunding ratio are randomly chosen from Azure SLAs \cite{azure}.
Each experiment lasts 100 minutes and is repeated 20 times, where the error bars paints the maximal, minimal and mean value.

>>>>

\section{Evaluation} \label{evaluation}
In this section, we use a small testbed and larger scale trace driven simulations  to evaluate the performance of $\mathsf{BATE}$. 
On the testbed, we also implement another two state-of-the-art TE algorithms considering network availability, i.e., FFC \cite{FFC} and TEAVAR \cite{Teavar}. 
For simulation, we implement more TE algorithms, including xxx. 
All codes for our implementation and evaluation will be published, 
so that interested readers can use them in their own environments or make further improvements.

@@

\textbf{A public cloud example}
We firstly evaluate a public cloud case.
Assume tenants arrive at the public cloud under poisson process with mean arrival rate 2 every minute and the duration of each bandwidth demand is under exponential distribution with a mean of 5 minutes.
Bandwidth demands between each node pair are under uniform distribution between 10Mbps and 50Mbps.
Every 1Mbps is sold 1$\$$.
%The profit of each tenant (i.e., $w_i$) is proportional to his/her total bandwidth demand.
Availability targets and refunding ratio are randomly chosen from Azure SLAs \cite{azure}.
Each experiment lasts 100 minutes and is repeated 20 times, where the error bars paints the maximal, minimal and mean value.
